*Prochlorococcus marinus* responses to light and oxygen

### 2024-03-13 Code/Manuscript_O2.Rmd
removed  equations out of chunk ```{=tex} ``` Seemed to be the problem

```{=tex}
\begin{equation}
  µ = \frac{ΔOD_{max} × ΔOD_{min} × exp^{(µ × t)}}{ΔOD_{max} + (ΔOD_{min} × exp^{((µ × t) - 1)})}
  (\#eq:GrowthRate)
\end{equation}
```

@@

```{=tex}
\begin{equation}
  P(λ) = A(λ) × E(λ) 
  (\#eq:WeightedPUR)
\end{equation}
```
PUR levels (µmol photons m^-2^ s^-1^) were calculated from
imposed PAR (µmol photons m^-2^ s^-1^) levels using the equation
\@ref(eq:PUR) from [@morelAvailableUsableStored1978]; where P(λ) is the
weighted PUR absorbance spectrum from equation \@ref(eq:WeightedPUR),
E(λ) is the imposed growth light emission spectrum from equation
\@ref(eq:WeightedPUR) and PAR is the imposed peak light level (µmol
photons m^-2^ s^-1^). Figure (\@ref(fig:PurParPlot)) shows the
calculated peak PUR (µmol photons m^-2^ d^-1^) vs. imposed
peak PAR (µmol photons m^-2^ s^-1^) for each strain and each spectral
waveband (nm).

```{=tex}
\begin{equation}
  PUR = \frac{\int_{400}^{700} P(λ)}{\int_{400}^{700} E(λ)} × PAR
  (\#eq:PUR)
\end{equation}
```
The applied photoperiods were delivered using the sinusoidal circadian
light function of the PSI Multicultivator to simulate light exposure
approximating sun rise through to sunset. The area under the sinusoidal
curves is equivalent to the area of a triangular photoregime of
equivalent photoperiod (Campbell, unpub), therefore the equation to
determine the cumulative diel PUR (µmol photons m^-2^ d^-1^) is one half
of the base (photoperiod) multiplied by the height (PUR) (Equation
\@ref(eq:SumPURDay)); where PUR is the usable light (µmol photons m^-2^ s^-1^) calculated from
equation \@ref(eq:PUR), 3600 is the time conversion from seconds to hour and photoperiod is the imposed
photoperiod (h).

```{=tex}
\begin{equation}
  Cumulative~diel~PUR = \frac{PUR × 3600 × Photoperiod}{2}
  (\#eq:SumPURDay)
\end{equation}
```
Figure \@ref(fig:OverlayPlots) provide visual representations of PUR,
the black solid line and shaded area, in relation to the imposed PAR,
the dotted line, under each imposed spectral wavebands for *P. marinus*
MED4 (A,B,C), SS120 (D,E,F) and MIT9313 (G,H,I). Figure
(\@ref(fig:PurParPlot)) shows the relationship between calculated PUR
vs. imposed PAR for each *P. marinus* and each spectral waveband.

>>>>

\begin{equation}
  µ = \frac{ΔOD_{max} × ΔOD_{min} × exp^{(µ × t)}}{ΔOD_{max} + (ΔOD_{min} × exp^{((µ × t) - 1)})}
  (\#eq:GrowthRate)
\end{equation}

@@

\begin{equation}
  P(λ) = A(λ) × E(λ) 
  (\#eq:WeightedPUR)
\end{equation}

PUR levels (µmol photons m^-2^ s^-1^) were calculated from
imposed PAR (µmol photons m^-2^ s^-1^) levels using the equation
\@ref(eq:PUR) from [@morelAvailableUsableStored1978]; where P(λ) is the
weighted PUR absorbance spectrum from equation \@ref(eq:WeightedPUR),
E(λ) is the imposed growth light emission spectrum from equation
\@ref(eq:WeightedPUR) and PAR is the imposed peak light level (µmol
photons m^-2^ s^-1^). Figure (\@ref(fig:PurParPlot)) shows the
calculated peak PUR (µmol photons m^-2^ d^-1^) vs. imposed
peak PAR (µmol photons m^-2^ s^-1^) for each strain and each spectral
waveband (nm).

\begin{equation}
  PUR = \frac{\int_{400}^{700} P(λ)}{\int_{400}^{700} E(λ)} × PAR
  (\#eq:PUR)
\end{equation}

The applied photoperiods were delivered using the sinusoidal circadian
light function of the PSI Multicultivator to simulate light exposure
approximating sun rise through to sunset. The area under the sinusoidal
curves is equivalent to the area of a triangular photoregime of
equivalent photoperiod (Campbell, unpub), therefore the equation to
determine the cumulative diel PUR (µmol photons m^-2^ d^-1^) is one half
of the base (photoperiod) multiplied by the height (PUR) (Equation
\@ref(eq:SumPURDay)); where PUR is the usable light (µmol photons m^-2^ s^-1^) calculated from
equation \@ref(eq:PUR), 3600 is the time conversion from seconds to hour and photoperiod is the imposed
photoperiod (h).

\begin{equation}
  Cumulative~diel~PUR = \frac{PUR × 3600 × Photoperiod}{2}
  (\#eq:SumPURDay)
\end{equation}

Figure \@ref(fig:OverlayPlots) provide visual representations of PUR,
the black solid line and shaded area, in relation to the imposed PAR,
the dotted line, under each imposed spectral wavebands for *P. marinus*
MED4 (A,B,C), SS120 (D,E,F) and MIT9313 (G,H,I). Figure
(\@ref(fig:PurParPlot)) shows the relationship between calculated PUR
vs. imposed PAR for each *P. marinus* and each spectral waveband.
